---
title: "RESTAURANT PROPOSAL 🍷🍽"
author: "BUSINESS TRAVEL"
date: 'From September 15th to 20th, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```

<br>
<br>
<br>


# September 16th - Cal Pinxo 

<iframe src="Cal Pinxo Palau de Mar/CalPinxo.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

## 🍽 Menu Options {.tabset .tabset-fade}

### Menu Atarazanas

    Crunchy aubergine with cane honey and soy
    
            Starters for share:
    Anchovies in Vinegar
    Seafood croquettes.
    Our Spanish potato salad
    Salmon tartar with trout caviar and shitake
    Baby fried shrimps
    Catalan tomato bread.
    -
    Rice of red shrimp with “fumet” stock
    -
    Catalan crème brûlée
    -
    White wine Freye (D.O. Penedès)
    Red Wine Viña Real (D.O. Rioja)
    Solán de Cabras water
    Nespresso coffee or tea
    Bread 
    
    Rates per peron: 52€ VAT inc
    
<hr>

### Menu Pescadores

    Welcome glass of cava, with potato, yucca and sweet potato chips
    
                    Starters for share:
    ”Esqueixada” cod salad with black olives
    ”Escalivada “cold roasted pepper, onion and aubergine salad over flat bread
    Cod fritters
    Seafood croquettes.
    Marinière Mussels casserole with tomato and white wine
    -
    Marinière Style rice Paella 
    or
    Noodles Paella with clams 
    or
    Black rice with squid ink and “all i oli” mayonnaise
    -
    Catalan crème brûlée 
    or
    Chocolate Brownie with vanilla ice cream 
    or
    Fruits skewer
    -
    White wine Barbara Forés (D.O. Terra Alta)
    Red wine Lobo Lover (D.O. Penedés (ECO)
    Water Solán de Cabras, Nespresso coffee or tea, Bread 
    
    Rates per peron: 60€ VAT inc (they can choose the main course on spot)
    
<hr>

# September 17th - Mirabé

<iframe src="Mirabe/Mirabe.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

## 🍽 Menu Options {.tabset .tabset-fade}

### Menu 1

    Beet and cottage cheese tart
    
    Timbale of roasted vegetables with red pepper sauce and kalamata olive oil.
    
    Hake loin confit at low temperature with fried artichokes, romesco sauce and green Mojo.
    
    Yogur mousse with red fruit and caramelized nuts
    
    Wine, beer, soft drinks and coffees.

    Rates per peron: 53€ VAT inc
    
<hr>

### Menu 2

    Smoked salmon roll with avocado and pineapple.
    
    Vegetable ravioli and goat cheese with creamy pesto sauce
    
    Lean pork fillet with caramelized onion, roast potatoes and spinach
    
    Catalan creme brulee with almond biscuit
    
    Wine, beer, soft drinks and coffees.

    Rates per peron: 53€ VAT inc
    
<hr>



# September 18th - Can Travi Nou

<iframe src="Can Travi Nou/CanTraviNou.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

## 🍽 Menu Options {.tabset .tabset-fade}

### Menu de l'Avia

    Fideuá, noodle paella with squid, mussels and prawns with alioli
    ***
    Toasted flat bread with tomato and olive oil
    ***
    Suckling pig knuckle cooked at low temperature with rosemary scented potatoes
    ***
    Black forest chocolate cake
    ***
    White Wine: Analivia (D.O. Rueda)*
    Red Wine: Raimat Clamor (D.O. Costers del Segre)*
    Mineral Waters
    *1 bottle of wine each 3 guests
    Coffee, decaffeinated, teas and herb teas

    Rates per peron: 54€ VAT inc
    
<hr>

### Menu Pepe

    TO SHARE
    Fresh sausage dices with white beans from Santa Pau
    Vermicelli noodle paella with squid and allioli  (garlic sauce)
    Homemade chicken croquettes
    Roasted vegetables (pepper and aubergine)
    Spanish omelette with onions and potato
    Padrón peppers with Maldon salt
    ***
    Toasted flat bread with tomato and olive oil
    ***
    MAIN COURSE TO CHOOSE IN ADVANCE
    Suckling pig knuckle cooked at low temperature with rosemary scented potatoes
    or
    Salmon suprême with lemon sauce and sauteed apples with caramel
    ***
    Black forest chocolate cake
    ***
    White Wine: Analivia (D.O. Rueda)*
    Red Wine: Raimat Clamor (D.O. Costers del Segre)*
    Mineral Waters
    *1 bottle of wine each 3 guests
    Coffee, decaffeinated, teas and herb teas

    Rates per peron: 57€ VAT inc
    
<hr>

### Menu Ocas

    Fish and sellfish cannelloni with crayfish sauce 
    ***
    Toasted flat bread with tomato and olive oil
    ***
    Melting veal roasted with mashed potato and truffle
    ***
    Crunchy chocolate
    ***
    White Wine: Analivia (D.O. Rueda)*
    Red Wine: Raimat Clamor (D.O. Costers del Segre)*
    Mineral Waters
    *1 bottle of wine each 3 guests
    Coffee, decaffeinated, teas and herb teas

    Rates per peron: 59€ VAT inc
    
<hr>


# September 19th - Alba Granados

<iframe src="Alba Granados/AlbaGranados.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

## 🍽 Menu Options {.tabset .tabset-fade}

### Classic Menu

    * to share*
    Our classic scrambled eggs with potatoes
    Alba's croquettes made of iberian ham D.O. Guijuelo
    Fried eggplants with honey "allioli"
    Russian salad
    
    *Main course*
    Tender Veal with potato parmentier and caramelizes apple
    or
    Grilled baby squids with "allioli" and santa pau beans
    
    *Desserts*
    Chocolate brownie with vanilla ice cream
    or 
    Mandarin sorbet
    
    Viña Pomal Crianza Magnum D.O Rioja
    Anima de Raimat Blanco Magnum D.O Costers del Segre
    Mineral water
    coffee or tea

    Rates per peron: 49€ VAT inc
    
<hr>

### Alba Menu

    * to share*
    Rocket Lettuce salad with pear, parmesan cheese and dates
    Our classic scrambles eggs with potatoes
    Alba's croquettes made of iberian ham D.O. Guijuelo
    Rock mussels cooked over coal and white wine
    Coca bread with escalibada and smaked sardine
    
    *Main course*
    Truffled cannelloni of roasted chicjen and beef
    or
    Grilled croakker with potato, butter and kale
    
    *Desserts*
    Catalan crwam with dry candied fruits 
    or 
    Pineapple carpaccio with orange marmalade
    
    Viña Pomal Crianza Magnum D.O Rioja
    Anima de Raimat Blanco Magnum D.O Costers del Segre
    Mineral water
    coffee or tea

    Rates per peron: 56,50€ VAT inc
    
<hr>


# 🚌 Transfer Rates

    * 50 seater bus transfer from Airport to Hotel Barceló Sants (from 8.00h to 20.00h): 215€ VAT inc
    * 50 seaters bus at disposal for dinner: 440€ VAT inc

<hr>

# ☑ Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business Travel
  
  * For a group of minimum 30 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
 
  
*****





