---
title: "RESTAURANT PROPOSAL"
author: "BUSINESS TRAVEL"
date: 'From September 15th to 20th, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```


Following you will find some nice restaurant suggestions walking distance from Hotel Barceló Sants but, as it is not a central hotel the restaurant offer in the area is small, that's why I am including a second label with restaurants that are located in other areas of the city but I think it worth to have a bus transfer.

## **Walking Distance restaurants** {.tabset .tabset-fade}

<iframe src="https://www.google.com/maps/d/embed?mid=1ZAv8PHfGZ6L3oa3M9Pry7_Vi1ks-XAvW&hl=es" width="100%" height="480"></iframe>

### Abrassame

<iframe src="Abrassame/Abrassame.html" frameborder="0" width="100%" height="1000" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 45€ VAT inc
<hr>

### Bodega Monumental

<iframe src="BodegaMonumental/BodegaMonumental.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 43€ VAT inc
<hr>

### Quinto Quinta

<iframe src="LaAzoteaQuintoQuinta/LaAzoteadeQuintooQuinta.html" frameborder="0" width="100%" height="1100"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 40€ VAT inc
<hr>

### MinE

I am waiting their answer - I will be able to have an answer by the end of August

    Menus from 44€ VAT inc

### Pan&Oli

I am waiting their answer - I will be able to have an answer next week

*****

## **Non Walking Distance restaurants** {.tabset .tabset-fade}

We would like to suggest some special restaurants, all of them are very good restaurants with something special: the location, the atmosphere, the food...

Mirabé haswonderful city views, Julivert Meu and Can Travi Nou is one of the best traditional catalan food in the city...

<iframe src="https://www.google.com/maps/d/embed?mid=1heyEGf89HtoStiweVys6KHCxItP__4UR&hl=es" width="100%" height="480"></iframe>

### Alba Granados

<iframe src="Alba Granados/AlbaGranados.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 49€ VAT inc
<hr>

### Arros i Peix

<iframe src="Arros i peix/ArrosiPeix.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 51€ VAT inc
<hr>

### Cal Pinxo Palau de Mar

<iframe src="Cal Pinxo Palau de Mar/CalPinxo.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 52,50€ VAT inc
<hr>

### Can Travi Nou

<iframe src="Can Travi Nou/CanTraviNou.html" frameborder="0" width="100%" height="1100"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 54€ VAT inc
<hr>

### Casa Carmen

<iframe src="Casa Carmen/CasaCarmen.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 55€ VAT inc
<hr>

### Julivert Meu

<iframe src="Julivert Meu/Julivert.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 44€ VAT inc
<hr>

### Mirabé

<iframe src="Mirabe/Mirabe.html frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

    Rates per peron: Menu including starters to share + main course + dessert + drinks + coffee, from 53€ VAT inc
<hr>

## Transfer Rates

    * 50 seater bus transfer from Airport to Hotel Barceló Sants (from 8.00h to 20.00h): 215€ VAT inc
    * 50 seaters bus at disposal for dinner: 440€ VAT inc

## Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business Travel
  
  * For a group of minimum 30 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
  
  * No reservation has been done.
  
*****





