---
title: "RESTAURANT PROPOSAL 🍷🍽"
author: "BUSINESS TRAVEL"
date: 'From September 15th to 20th, 2019'
output:
 
  html_document:
    css: FORMATO.css
    highlight: textmate
    theme: cosmo
    toc: yes
    toc_float: yes
---

<script> 
    $(document).ready(function() { 
    $head = $('#header'); 
    $head.prepend('<A href = https://www.cuttingedge-events.com><img src ="LOGO.png" width="150" vspace="50" align="right"></A>') 
    }); 
</script> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```


```{r libraries}
library(readxl)
library(dplyr)
library(knitr)
library(timevis)

```

<br>
<br>
<br>

# Map

<iframe src="https://www.google.com/maps/d/embed?mid=1heyEGf89HtoStiweVys6KHCxItP__4UR&hl=es" width="100%" height="550"></iframe>

<br>
<br>


# September 16th - 20.00h  - Cal Pinxo 

<iframe src="Cal Pinxo Palau de Mar/CalPinxo.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>


### Customized menu

    Welcome glass of cava
    -
    *Starters to share*
    "Esqueixada" ( tomato salad with onion and cod fish)
    Toasted bread with charcoal grilled pepper and aubergine and salty anchovie from Cantabrico
    Cod fish fritters
    Sea-food croquettes
    Mussels with tomato and white wine sauce
    -
    *Main course to choose*
    Rice with white prawn fumet
    or
    Grilled Entrecote
    -
    Fruit skewer
    or
    Catalan crème brûlée
    -
    White wine Barbara Fores (D.O Terra alta)
    Red Wine Lobo Lover (D.O Penedes (ECO))
    Solán de Cabras water
    Nespresso coffee or tea
    Bread 
    
    Rates per peron: 55€ VAT inc
    


# September 17th - 20.00h - Taller de Tapas Rambla Catalunya

<iframe src="TALLER DE TAPAS/Taller de Tapas.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>


## 🍽 Menu Options {.tabset .tabset-fade}

### MENU TALLER 

    TO SHARE
    Toasted coca bread rubbed with tomato and extra virgin olive oil
    Cured best Jabugo ham “Juan Manuel” D.O. Guijuelo
    Selection of Spanish cheeses with quince jelly
    Oven roasted red pepper, onion and aubergine with Cantabrian anchovies
    Homemade hummus with pita bread
    &
    Crispy aubergine with honey and lime
    Homemade Jabugo ham croquettes
    “Patatas bravas” with garlic mayonnaise and spicy sauce
    &
    Sautéed chickpeas, fresh spinach and Iberian pancetta
    Grilled green asparagus with cherry tomato and a walnut dressing
    &
    Grilled farmhouse sausage with Santa Pau White beans
    Grilled squid with lemon dressing
    Grilled chicken kebab marinated with herbs and spices

    DESSERTS
    Catalan crème brûlée
    Almond tart with cinnamon ice-cream

    CELLER
    White wine: Parató (D.O. Penedès)
    Red wine: Finca Renardes (D.O. Penedès)
    Mineral water
    Coffee or tea
    
    Rates per person: 43€ VAT inc

### MENU DEL PI

    TO SHARE
    Toasted coca bread rubbed with tomato and extra virgin olive oil
    Cured best Jabugo ham “Juan Manuel” D.O. Guijuelo
    Rocket salad with Nuri´s goat cheese, quince jelly and toasted almonds
    Homemade hummus with pita bread
    &
    Crispy aubergine with honey and lime
    Andalusian style fried squid with lime mayonnaise
    Homemade Jabugo ham croquettes
    “Patatas bravas” with garlic mayonnaise and spicy sauce
    &
    Pan-steamed mussels with Mediterranean herbs
    Grilled green asparagus with cherry tomato and a walnut dressing
    Sautéed wild seasonal mushrooms
    Majorcan sobrasada sausage omelette topped with garlic mayonnaise
    Chicken wings with garlic, lemon and chilli
    &
    Grilled prawns with extra virgin olive oil and Maldon salt
    Grilled best sirloin steak with garlic thyme and chilli

    DESSERTS
    Catalan crème brûlée
    Dark and White chocolate mousse

    DRINKS
    White wine: Afortunado (D.O. Rueda)
    Red wine: Basagoiti, crianza (D.O. Rioja)
    Mineral water
    Coffee or tea
    
    Rates per person: 47,50€ VAT inc

### MENU STA MARIA

    TO SHARE
    Toasted coca bread rubbed with tomato and extra virgin olive oil
    Cured best Jabugo ham “Juan Manuel” D.O. Guijuelo
    Rocket salad with Nuri´s goat cheese, quince jelly and toasted almonds
    Homemade hummus with pita bread
    Langoustines with tartar sauce
    &
    Crispy aubergine with honey and lime
    Homemade Jabugo ham croquettes
    “Patatas bravas” with garlic mayonnaise and spicy sauce
    &
    Pan-steamed mussels with Mediterranean herbs
    Grilled green asparagus with cherry tomato and a walnut dressing
    Galician style octopus with smoked paprika and extra virgin olive oil
    Grilled squids and prawns with garlic dressing
    &
    Grilled special Iberian pork fillet “secreto” with mojo sauce
    Grilled tuna from Boquería market with avocado tomato and basil
    
    DESSERTS
    Catalan crème brûlée
    Dark and White chocolate mousse
    
    DRINKS
    White wine: Afortunado (D.O. Rueda)
    Red wine: Basagoiti, crianza (D.O. Rioja)
    Mineral water
    Coffee
    
    Rates per person: 50€ VAT inc

### MENU BORN

    TO SHARE
    Toasted coca bread rubbed with tomato and extra virgin olive oil
    Cured best Jabugo ham “Juan Manuel” D.O. Guijuelo
    Oven roasted red pepper, onion and aubergine with Cantabrian anchovies
    Langoustines with tartar sauce
    Homemade hummus with pita bread
    &
    Fried and crispy artichoke hearts with romesco sauce
    Fried battered cod with mango tartar
    Homemade Jabugo ham croquettes
    “Patatas bravas” with garlic mayonnaise and spicy sauce
    &
    Majorca sobrasada sausage omelette topped with garlic mayonnaise
    Sizzling prawns cooked in a pot with garlic, chilli and mountain herbs
    Galician style octopus with smoked paprika and extra virgin olive oil
    &
    Grilled special Iberian pork fillet “secreto” with mojo sauce
    Grilled tuna from Boquería market with avocado tomato and basil
    Mini beef burger with caramelized red onion and brie cheese
    
    DESSERT
    Catalan crème brûlée
    Dark and White chocolate mousse
    
    DRINKS
    White wine: Marqués Alella (D.O. Alella)
    Red wine: Basagoiti, crianza (D.O. Rioja)
    Cava Parató Brut
    Mineral water
    Coffee

    Rates per person: 62,50€ VAT inc



# September 18th - 20.00h - Can Travi Nou

<iframe src="Can Travi Nou/CanTraviNou.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>


## Menu Pepe

    TO SHARE
    Fresh sausage dices with white beans from Santa Pau
    Vermicelli noodle paella with squid and allioli  (garlic sauce)
    Homemade chicken croquettes
    Roasted vegetables (pepper and aubergine)
    Spanish omelette with onions and potato
    Padrón peppers with Maldon salt
    ***
    Toasted flat bread with tomato and olive oil
    ***
    MAIN COURSE TO CHOOSE 
    Suckling pig knuckle cooked at low temperature with rosemary scented potatoes
    or
    Salmon suprême with lemon sauce and sauteed apples with caramel
    ***
    Black forest chocolate cake
    ***
    White Wine: Analivia (D.O. Rueda)*
    Red Wine: Raimat Clamor (D.O. Costers del Segre)*
    Mineral Waters
    *1 bottle of wine each 3 guests
    Coffee, decaffeinated, teas and herb teas

    Rates per peron: 57€ VAT inc -they can choose main in the restaurant -
    
<hr>



# September 19th - 20.00h - Alba Granados

<iframe src="Alba Granados/AlbaGranados.html" frameborder="0" width="100%" height="1100" scrolling="no"></iframe>

## 🍽 Menu Options {.tabset .tabset-fade}

### Classic Menu

    * to share*
    Our classic scrambled eggs with potatoes
    Alba's croquettes made of iberian ham D.O. Guijuelo
    Fried eggplants with honey "allioli"
    Russian salad
    
    *Main course*
    Tender Veal with potato parmentier and caramelizes apple
    or
    Grilled baby squids with "allioli" and santa pau beans
    
    *Desserts*
    Chocolate brownie with vanilla ice cream
    or 
    Mandarin sorbet
    
    Viña Pomal Crianza Magnum D.O Rioja
    Anima de Raimat Blanco Magnum D.O Costers del Segre
    Mineral water
    coffee or tea

    Rates per peron: 49€ VAT inc -they can choose main and dessert in the restaurant -
    
<hr>

### Alba Menu

    * to share*
    Rocket Lettuce salad with pear, parmesan cheese and dates
    Our classic scrambles eggs with potatoes
    Alba's croquettes made of iberian ham D.O. Guijuelo
    Rock mussels cooked over coal and white wine
    Coca bread with escalibada and smaked sardine
    
    *Main course*
    Truffled cannelloni of roasted chicjen and beef
    or
    Grilled croakker with potato, butter and kale
    
    *Desserts*
    Catalan crwam with dry candied fruits 
    or 
    Pineapple carpaccio with orange marmalade
    
    Viña Pomal Crianza Magnum D.O Rioja
    Anima de Raimat Blanco Magnum D.O Costers del Segre
    Mineral water
    coffee or tea

    Rates per peron: 56,50€ VAT inc -they can choose main and dessert in the restaurant -
    
<hr>


# 🚌 Transfer Rates

    * 50 seater bus transfer from Airport to Hotel Barceló Sants (from 8.00h to 20.00h): 215€ VAT inc
    * 50 seaters bus at disposal for dinner: 440€ VAT inc

<hr>

# ☑ Terms & Conditions

  * Rates valid for 2019.
  
  * Net rates for Business Travel
  
  * For a group of minimum 30 pax.
  
  * Cutting Edge Events management fee including in the detailed rates
  
  * VAT included. 
 
  
*****





